cardinalR: Generating interesting high-dimensional data structures

### 2025-08-24 paper-cardinalR.Rmd
Added projections

gridedsphere_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "d1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

gridedsphere_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "d2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

gridedsphere_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "d3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

clusteredspheres_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "e1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

clusteredspheres_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "e3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

hemisphere_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "f1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

>>>>

gridedsphere_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.75, 0.7), 
  title = "d1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

gridedsphere_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.65), 
  title = "d2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

gridedsphere_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.62), 
  title = "d3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

clusteredspheres_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.75, 0.7), 
  title = "e1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

clusteredspheres_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.6, 0.62), 
  title = "e3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

hemisphere_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.75, 0.7), 
  title = "f1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)
